New seismological constraints on the available parameter space of macroscopic dark matter

### 2016-08-30 Draft.tex
Update

This procedure is repeated for 17 values of $D$ spaced evenly by $100\,\te{km}$. The average fraction of detectable surface area is then approximately
\begin{align}
\scr F = \sum_D\f{\scr F_D D}{D}\,.
\end{align}
If there are $n$ lunar seismometers, we suppose that each occupies its own HEALPix pixel. Define $m = \scr Fn_\te{pix}$, the average number of pixels with detectable frequency. If $n+m\geq n_\te{pix}$, then detection is guaranteed. Otherwise, if $\scr M$ Macros impact the moon, the likelihood of any of them being detected is
\begin{align}
\scr P &= 1-\ps{\f{(n_\te{pix}-n)!(n_\te{pix}-m)!}{n_\te{pix}!(n_\te{pix}-n-m)!}}^{\scr M}\,.
\end{align}
\subsection{Analytic Upper Bound}
If the energy of a ray from every point along the line hitting a single pixel (with no reflection, refraction, or attenuation) is less than the displacement threshold, there is no chance of detection and no need to run the simulation. (If two rays from the same point on the line source hit the same pixel as $n_\te{side}\to\infty$, then they must be the same ray). Thus, we bound the displacement by
\begin{align}
u\leq\sqrt{\f{\Xi E}{\pi^2\rho k v_p^2 R_\te{Moon}^2}}
\end{align}
This expression is independent of the choice of $n_\te{side}$. For the triangle wave, we need not test $\sigma_X\leq 4\times 10^{-11}\te{m}^2$.
\section{Results}
Data has been generated but not run through the analysis routine yet. Preliminary results suggest that the computer analysis will not produce results much stronger than (30).
\section{Conclusion}
For Macros with mass to area ratio sufficient to pass nearly unimpeded through the Moon, and in particular nuclear dense objects such as strange quark nuggets, we have demonstrated that seismological constraints are insufficient to rule them out. In order to use the Moon as a low noise detector for high density Macros, it would be necessary to increase the usable frequency range of seismometers to several hundred Hertz. However, since the Moon (and Earth) preferentially attenuate higher frequency modes, it is unlikely that measuring high frequencies would greatly improve sensitivity to these types of impacts.

On the other hand, increasing the lunar seismometer sensitivity to small displacements would increase the volume of Macro parameters one could rule out. That said, it is uncertain whether seismic noise at such small displacements would make Macro impacts indistinguishable from the background.
\section{Acknowledgements}
The author would like to thank SOURCE for supporting this research.
\bibliography{Macro-Impact}{}
\bibliographystyle{apsrev4-1}
\end{document}

>>>>

This procedure is repeated for 17 values of $D$ spaced evenly by $100\,\te{km}$. The average fraction of detectable surface area is then approximately
\begin{align}
\scr F = \sum_D\f{\scr F_D D}{D}\,.
\end{align}
If there are $n$ lunar seismometers, we suppose that each occupies its own HEALPix pixel. Define $m = \scr Fn_\te{pix}$, the average number of pixels with detectable frequency. If $n+m\geq n_\te{pix}$, then detection is guaranteed. Otherwise, if $\scr M$ Macros impact the moon, the likelihood of any of them being detected is
\begin{align}
\scr P &= 1-\ps{\f{(n_\te{pix}-n)!(n_\te{pix}-m)!}{n_\te{pix}!(n_\te{pix}-n-m)!}}^{\scr M}\,.
\end{align}
\subsection{Analytic Upper Bound}
If the energy of a ray from every point along the line hitting a single pixel (with no reflection, refraction, or attenuation) is less than the displacement threshold, there is no chance of detection and no need to run the simulation. (If two rays from the same point on the line source hit the same pixel as $n_\te{side}\to\infty$, then they must be the same ray). Thus, we bound the displacement by
\begin{align}
u\leq\sqrt{\f{\Xi E}{\pi^2\rho k v_p^2 R_\te{Moon}^2}}
\end{align}
This expression is independent of the choice of $n_\te{side}$. For the triangle wave, we need not test $\sigma_X\leq 4\times 10^{-11}\te{m}^2$.
\section{Results}
Data has been generated but not run through the analysis routine yet. Preliminary results suggest that the computer analysis will not produce results much stronger than (30).
\section{Conclusion}
For Macros with density sufficient to pass nearly unimpeded through the Moon, and in particular nuclear dense objects such as strange quark nuggets, we have demonstrated that seismological constraints are insufficient to rule them out. Since the Moon (and Earth) preferentially attenuate higher frequency modes, it is unlikely that measuring high frequencies would greatly improve sensitivity to these types of impacts. On the other hand, increasing the lunar seismometer sensitivity to small displacements would allow one to use seismological evidence to rule out high density Macros. That said, it is uncertain whether seismic noise at such small displacements would make Macro impacts indistinguishable from the background.
\section{Acknowledgements}
The author would like to thank SOURCE for supporting this research.
\section{Summer Reflection}
My research this summer will be very important when I make my case to graduate schools that I am capable of doing independent research and problem solving. This project will likely be developed into my capstone, and we will try to publish this work. For next year's students, drink lots of coffee.
\bibliography{Macro-Impact}{}
\bibliographystyle{apsrev4-1}
\end{document}
